Paper 2: Vitamin D

### 2018-05-03 doc/vitaminD.Rmd
changed labels on boxplots to include values

# Clean data
vitd <- ds %>% 
  filter(fVN == "Baseline") %>% 
  select(vitdStatus, udbpCr, UDBP) %>%
  na.omit()

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot("vitdStatus", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  # dplyr::filter(acrStatus != "Normoalbuminuria") %>% 
  scatter_plot("log(udbpCr)", "log(VitaminD)", 
                "log uVDBP:cr (μg/mmol)",
               "log serum 25(OH)D (nmol/L)")

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCrBase",
            covars = c("YearsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "BMI", "MET", "dmStatus", "Season")) %>% 
            # intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCr",
            covars = c("YearsFromBaseline", "ageBase", "Sex", "Ethnicity", "BMI",
                       "MET", "dmStatus", "Season")) %>% 
            # intvar = "Season") %>% 
  mason::polish_renaming(rename_gee_vitd)

>>>>

# Clean data
vitd <- dsBase %>% 
  dplyr::mutate(vitdLabels = ifelse(vitdStatus == "Sufficient", "Sufficient \n(≥75 nmol/L)",
                                   ifelse(vitdStatus == "Insufficient", "Insufficient \n(50 - 75 nmol/L)",
                                          "Deficient \n(<50 nmol/L)")),
                vitdLabels = factor(vitdLabels,
                                   levels = c("Sufficient \n(≥75 nmol/L)",
                                              "Insufficient \n(50 - 75 nmol/L)",
                                              "Deficient \n(<50 nmol/L)"),
                                   ordered = TRUE)) %>%
  select(vitdStatus, vitdLabels, udbpCr, UDBP) %>%
  na.omit()

# Box plot of uVDBP in different albuminuria categories
vitd %>% 
  box_plot_slides("vitdLabels", "log(udbpCr)", 
            "Vitamin D Status",
            "log uVDBP:cr (μg/mmol)")

@@

dsBase %>% 
  # dplyr::filter(acrStatus != "Normoalbuminuria") %>% 
  scatter_plot_transparent("log(udbpCr)", "log(VitaminD)", 
                "log uVDBP:cr (μg/mmol)",
               "log serum 25(OH)D (nmol/L)")

@@

gee_vitd_baseline <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCrBase",
            covars = c("YearsFromBaseline", "ageBase", "Sex", 
                       "Ethnicity", "BMI", "MET", "dmStatus", "Season"),
            intvar = "BMI") %>%
  mason::polish_renaming(rename_gee_vitd)

@@

gee_vitd <- ds %>% 
  prep_mason_data_vitd() %>% 
  mason_geeplot(y = "lVitD",
            x = "udbpCr",
            covars = c("YearsFromBaseline", "ageBase", "Sex", "Ethnicity", "BMI",
                       "MET", "dmStatus", "Season"), 
            intvar = "BMI") %>%
  mason::polish_renaming(rename_gee_vitd)
